Compiling refinement types to dependent types

### 2020-07-09 tex/paper.tex
Don't need a special bullet for the fst/snd functions
Sort of got the syntax for case
Add a note on the dummy parameters

\newNTclass{nonterm}
\newnonterm e \varepsilon
\newnonterm{es}{\varepsilon}
\newnonterm{ec}{\hat\varepsilon}
\newnonterm r \rho
\newnonterm{ts}{\tau}
\newnonterm s s
\newnonterm B B
\newnonterm G \Gamma
\newnonterm{GC}{\hat\Gamma}
\newnonterm{binop}{\odot}

@@

\begin{figure}[ht]
  \footnotesize
  \begin{subfigure}{.6\textwidth}
    \nonterms{es}
    \caption{Term level}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \nonterms{G,r,B,ts}
    \caption{Type level}
  \end{subfigure}
  \caption{Surface language syntax}
  \label{fig:surface_syntax}
\end{figure}

@@

@@

\begin{itemize}
  \item Non-dependent function type:
    \[
      \tau_1 \rightarrow \tau_2 \triangleq \Pi \_ : \tau_1. \tau_2.
    \]
  \item Dependent pair type, or $\Sigma$-type, with the first component being a value $x$ of type $\tau$ and the second component being of type $P x$:
    \[
      \{ x : \tau\ **\ P x \} \triangleq \Pi \alpha : \star. (\Pi x : \tau. P x \rightarrow \alpha) \rightarrow \alpha.
    \]
  \item Accessing the first and second component of the dependent pair:
    \[
      \text{fst} \triangleq TODO,
    \]
    \[
      \text{snd} \triangleq TODO.
    \]
  \item Non-dependent pair type:
    \[
      (\tau_1, \tau_2) \triangleq \{ x : \tau_1\ **\ (\lambda \_ : \tau_1. \tau_2) x \}.
    \]
  \item Equality of expressions $\nonterm{ec}_1, \nonterm{ec}_2$ of type $S$:
    \[
      \nonterm{ec}_1 \equiv \nonterm{ec}_2 \triangleq \Pi P : S \rightarrow \star. (P x \rightarrow P y, P y \rightarrow P x).
    \]
    Careful reader will recognize this as the Leibniz equality \cite{FindSomethingForThis}.
\end{itemize}

>>>>

\newNTclass{nonterm}
\newnonterm e \varepsilon
\newnonterm{es}{\varepsilon}
\newnonterm{ec}{\hat\varepsilon}
\newnonterm r \rho
\newnonterm{ts}{\tau}
\newnonterm s s
\newnonterm l l
\newnonterm B B
\newnonterm G \Gamma
\newnonterm{GC}{\hat\Gamma}
\newnonterm{binop}{\odot}

@@

\begin{figure}[ht]
  \footnotesize
  \begin{subfigure}{.6\textwidth}
    \nonterms{es,l}
    \caption{Term level}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \nonterms{G,r,B,ts}
    \caption{Type level}
  \end{subfigure}
  \caption{Surface language syntax}
  \label{fig:surface_syntax}
\end{figure}

@@

The surface language might also have other base types (for example, $\mathbf{Int}$),
elements of syntax (like numbers and operations on them)
as well as typing rules relating those,
but we omit them for the sake of brevity.

Note that although the syntax does not allow refining function types or ADTs,
it does not restrict the expressive power of the language.
For instance, a refinement on a function that we might otherwise wish to write as
\[
  (x : \mathbf{Int}) \rightarrow \{ v : \mathbf{Int} \rightarrow \mathbf{Int} | v x = 0 \} \rightarrow \mathbf{Int}
\]
might instead be expressed via a dummy parameter:
\[
  (x : \mathbf{Int}) \rightarrow (f : \mathbf{Int} \rightarrow \mathbf{Int}) \rightarrow \{ \_ : \mathbf{Unit} | f x = 0 \} \rightarrow \mathbf{Int}
\]

@@

\begin{itemize}
  \item Non-dependent function type:
    \[
      \tau_1 \rightarrow \tau_2 \triangleq \Pi \_ : \tau_1. \tau_2.
    \]
  \item Dependent pair type, or $\Sigma$-type, with the first component being a value $x$ of type $\tau$ and the second component being of type $P x$:
    \[
      \{ x : \tau\ **\ P x \} \triangleq \Pi \alpha : \star. (\Pi x : \tau. P x \rightarrow \alpha) \rightarrow \alpha,
    \]
    with the corresponding accessors:
    \[
      \text{fst} \triangleq TODO,
    \]
    \[
      \text{snd} \triangleq TODO.
    \]
  \item Non-dependent pair type:
    \[
      (\tau_1, \tau_2) \triangleq \{ x : \tau_1\ **\ (\lambda \_ : \tau_1. \tau_2) x \}.
    \]
  \item Equality of expressions $\nonterm{ec}_1, \nonterm{ec}_2$ of type $S$:
    \[
      \nonterm{ec}_1 \equiv \nonterm{ec}_2 \triangleq \Pi P : S \rightarrow \star. (P x \rightarrow P y, P y \rightarrow P x).
    \]
    Careful reader will recognize this as the Leibniz equality \cite{FindSomethingForThis}.
\end{itemize}
